---
title: "Lightning Summary: \nStarting with Tidy Text"
author: "Katherine Simeon"
date: "June 26, 2018"
output: 
  slidy_presentation:
    highlight: NULL
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidytext)
library(dplyr)
library(stringr)
library(rtweet)
library(wordcloud2)
library(ggplot2)
```

## Tidy Format 
  
- Each variable is a column   
- Each observation is a row - for text, this means one **token** per row (or one meaningful unit of text, e.g. word)  
- Each type of observational unit is a table      
  

## Let's get our data

Let's look at **#RLadies** on Twitter during the past week:  
  
```{r, echo=TRUE}
rladies_tweets <- as_tibble(read.csv("rladies_twitter_data.csv",stringsAsFactors = FALSE))
# creates a tibble, see more info at vignettes("tibble")
```

## Let's look at our data

```{r, echo=TRUE}
head(rladies_tweets)
```

## Tokenization
  
Let's make our data *one token per row*:   
  
```{r, echo=TRUE,message=FALSE}
rladies_table <- rladies_tweets %>% 
  unnest_tokens(word, text)

# Comparing dimensions
dim(rladies_tweets) # each row is a tweet
dim(rladies_table) # each row is a word
```
  
  
## Filtering stop words    
  
The tidytext package has a dataset of **stop words** (extremely common words that might not be informative for analysis) that we can use to filter our data:  
  
```{r, echo=TRUE,message=FALSE}
data(stop_words) # get stop words
rladies_table <- rladies_table %>% # Filter out of r_ladies table
  anti_join(stop_words)  

rladies_table <-rladies_table %>% # Remove other words (specified)
  filter(!word %in% c('t.co', 'https','de','el', 'en'))
```
  
## Let's do a word count  
  
```{r, echo=TRUE}
rladies_wc <- rladies_table %>%
  count(word, sort = TRUE) 
head(rladies_wc)
```

## Let's make a word cloud!  
  
Using the **wordcloud2** package:   
  
```{r, echo=TRUE}
# Creating an R-Ladies Color Palette (from the ggplot2 theme of R-Ladies Global)
rladies_palette <- c("#88398A","#D3D3D3","#181818","#562457","#88398A")
wordcloud2(rladies_wc, size=2, shape="star", color=rladies_palette)
```
  
## Sentiment Analysis  
  
The tidytext package has 3 lexicons for sentiment analysis:  
  
- AFINN -- numerical scale from -5 to 5  
- Bing -- binary categorization (postive or negative)  
- NRC -- Yes/no categorization of:  
    + Positive  
    + Negative  
    + Anger  
    + Anticipation  
    + Disgust  
    + Fear  
    + Joy  
    + Sadness  
    + Surprise  
    + Trust  
  
  
## Let's try it with NRC (like in the book)  
  
```{r, echo=TRUE, message=FALSE}
nrc_joy <- get_sentiments("nrc") %>% 
  filter(sentiment == "joy")

rladies_joy <- rladies_table %>%
  inner_join(nrc_joy) %>%
  count(word,sort=TRUE)

rladies_joy
```
  